My title

### 2024-11-26 paper/paper.qmd
update model section

For this analysis, I employed a Logistic Regression Model to assess the likelihood of an individual not being married (outcome variable) based on several demographic and socioeconomic predictors (predictor variables). This model was chosen due to the binary nature of the outcome variable, which distinguishes between individuals who are "Not Married" versus those who are married (including divorced, widowed, or separated)..

@@

### Priors Explanation
In this model, normal priors with a mean of 0 and a standard deviation of 2.5 are assigned to all coefficients and the intercept. This choice reflects neutrality, implying no prior expectation of direction or magnitude for the coefficients.

@@

### Model justification

@@

>>>>

For this analysis, I employed a Logistic Regression Model to assess the likelihood of an individual not being married (outcome variable) based on several demographic and socioeconomic predictors (predictor variables). This model was chosen due to the binary nature of the outcome variable, which distinguishes between individuals who are "Not Married" versus those who are married (including divorced, widowed, or separated).

@@

### Priors Explanation

In this model, normal priors with a mean of 0 and a standard deviation of 2.5 are assigned to all coefficients and the intercept. This choice reflects neutrality, implying no prior expectation of direction or magnitude for the coefficients.

@@

## Model justification

The logistic regression model was chosen for this study due to its suitability for predicting binary outcomes, in this case, whether an individual is categorized as "Not Married" or not. Logistic regression is widely used in social science research to understand relationships between a binary dependent variable and multiple independent variables, making it an ideal choice for analyzing marital status. This model allows for a straightforward interpretation of the effects of predictors, such as age, income, education, and gender, through odds ratios, providing insight into the likelihood of being "Not Married." The dataset contains a mix of continuous and categorical variables, and logistic regression can handle this diversity effectively. Additionally, its theoretical simplicity ensures that the analysis remains interpretable while maintaining robustness. The choice of this model aligns with the study’s goal of identifying significant factors associated with non-marriage in the U.S., providing actionable insights while being grounded in established statistical methods. Despite its assumptions, such as linearity in the log-odds and independence of observations, logistic regression offers the flexibility to incorporate interaction terms and account for a range of predictor variables, making it a powerful tool for this research.

##Model Validation

@@

## Model Assumptions
1. **Linearity**: The log odds of the outcome are linearly related to the predictors.
2. **Independence**: Observations are independent of each other.
3. **No Multicollinearity**: Predictors are not highly correlated.
4. **No Outliers or Influential Points**: Checked through residual analysis.
